---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# Xplorer: Convenient Data Exploration with see() and browse()

Xplorer provides two simple functions to facilitate the exploration of datasets in R, [`see()`](#see) and [`browse()`](#browse).

## see() {#see}

`see()` prints the following details of an object to the console:

- attributes (useful to inspect labels)
- class, typeof, mode, storage.mode
- table (frequency and percentage of values)
- summary statistics

There are several other packages which attempt to do someting similar, but none of them offers the ease of use and thourough inspection of ojects. For example, base R offers the functions `summary()`, `str()` and `structure()`. However, each of those is limited in what they display and leave other aspects untouched. `see()` combines a number of functions that would have to be invoked seperately and mirrors Stata's 'codebook'. 

`see()`is an S3 generic and currently comes with the following data types:

* character
* factor
* numeric
* data.frame
* labelled
* default (all other types)

#### Example

```{r}
library("Xplorer")

# Create example data
numeric.labelled <- c(1, 2, 2, 3, 3, 3, 4, 4, 4, 4)
attributes(numeric.labelled)$label <- "mylabel"

# see the object
see(numeric.labelled)
```


## browse() {#browse}

The aim of `browse()` is to create a data.frame that allows you to use the search field in the Rstudio `View()` function to search for variables based on their names or values, which is currently not possible. In particular if a dataset is very large and no comprehensive codebook is available, quickly searching for variable names makes finding variables of interest much easier. 

If you are not working in Rstudio, `View()` may not work in the same way and may not offer a search option. Hence `browse()` does not call `View()` directly. Instead, store the data in a new object first, which then can be opened with `View()` in Rstudio. `browse()` can also be called on a data.frame directly to print the output to the console.

#### Example

```{r}
library("Xplorer")

# Create an example data.frame and add some variable labels
data(mtcars)
attributes(mtcars$mpg)$label <- "Miles/(US) gallon"
attributes(mtcars$cyl)$label <- "Number of cylinders"
attributes(mtcars$disp)$label <- "Displacement (cu.in.)"
attributes(mtcars$hp)$label <- "Gross horsepower"
attributes(mtcars$drat)$label <- "Rear axle ratio"
attributes(mtcars$wt)$label <- "Weight (1000 lbs)"
attributes(mtcars$qsec)$label <- "1/4 mile time"
attributes(mtcars$vs)$label <- "V/S"

# Call browse() directly...
browse(mtcars)

# ...or assign to df and open with View()
df <- browse(mtcars)
```
Then use `View(df)` and use the search field to search variable names and labels. Or, even simpler, just use `View(browse(mtcars))`.

## Installation

You can install Xplorer from GitHub with:
```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("fschaff/Xplorer")
```

Please report issues or requests for additional functionality to https://github.com/fschaff/Xplorer/issues.
