---
title: "Inspect Objects (i.e. variables) with see()"
author: "Florian Simon Schaffner"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Inspect objects with see()}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

This vignette explains the rationale behind writing `explorer::see()`, compares it to other packages and provides examples for using it.

## Why write see?

There are several other packages which attempt to do someting similar, but none of them offers the ease of use and thourough inspection of oject aspects. 

For example, base R offers the functions `summary()`, `str()` and `structure()`. However, each of those is limited in what they display and leave other aspects untouched. 

No function exists that does what it does. It cleverly combines functions that would have to be invoked seperately and mirrors Stata's 'codebook'. 
`see()` prints the following details of variable to the console:

- attributes (useful to inspect labels)
- class, typeof, mode, storage.mode
- table (frequency and percentage of values)
- summary statistics

```{r}
library("explorer")
see(mtcars$mpg)
```




## Examples

### Attributes (e.g. labels)

```{r}
# Create example data
numeric.labelled <- c(1, 2, 2, 3, 3, 3, 4, 4, 4, 4)
attr(numeric.labelled, "label") <- "mylabel"

see(numeric.labelled)
```

### Class, Type, Mode and Storage Mode
I am frequently interested to know the class or type of an object. To detect each it needed several different commands. They have to be typed each and this is time consuming. With `see()` all of them get displayed. 

```{r}
class(numeric.labelled)
typeof(numeric.labelled)
see(numeric.labelled)
```


### Values, Frequency

### summary statistics

```
Example of an unevaluated textbox
```
